\section{Problem}

We wish to protect a document storage system, which backs an
application where clients collaborate on documents, from
ransomware attacks on the servers. We need to tolerate situations
where an attacker can access the persistent storage backing this
system, and replace it either with an outdated version or an
encrypted version.

\subsection{Requirements}
The solution should:
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
    \item Tolerate a subset of servers with tampered
        persistent storage;
    \item Allow for deletions from the file (after being
        agreed by a sufficient subset of the collaborators);
    \item Tolerate a subset of malicious collaborators, which
        may try to delete the file or corrupt it;
    \item Allow for concurrent collaboration of documents;
    \item Provide confidentiality of the documents: it should
        be impossible for the servers, other clients or a
        malicious attackers to see the cleartext contents of
        the file;
    \item Provide integrity of the documents: it should
        be impossible for the servers, other clients or a
        malicious attackers to change the content of
        the file;
    \item Allow for membership changes: if a client is added,
        it can see the full history of the file; if a client
        is removed, it should not be able to see new
        modifications.
    \item Provide non-repudiability of specific document changes;
\end{itemize}

\newpage

\subsection{Trust Assumptions}
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
    \item We assume the server code (written by us) to be correct.
    
    \item We assume that the persistent storage backing the server
	can be changed by a malicious administrator.

    \item Unauthenticated clients are fully untrusted by the servers.

    \item Authenticated clients are not assumed to follow the protocol
        correctly.

    \item Servers are fully untrusted by clients for confidentiality.
        For data integrity, clients do trust a server quorum.

    \item Clients partially trust their collaborators: it should
	be possible for a majority of clients to rollback changes
	performed by a malicious client.

    \item Collaborators fully trust the owner of the file to change
	the membership of the file.

    \item There is a trusted administrator which remotely provisions
	the servers with their keys for secure communication with
        clients/other servers.

    \item Clients and Servers trust the CA for certification of server's
	keys for the effects of having secure channels
	(in client-server and server-server communication).

    \item Everyone trusts the CA for certification of client's keys for
        non-repudiation of other's changes.
\end{itemize}
